Preliminary Thesis Defence

### 2013-11-13 draft.Rnw
functioning refsections
update frontpage

\title{Preliminary Thesis Defence}
%\subtitle{
%\begin{tabular}{rl}
%Supervisor:&Jean-Louis Arcand\footnote{Professor of Economics, The Graduate Institute, Geneva; Director, Centre for Finance and Development; jean-louis.arcand@graduateinstitute.ch}\\
%Second Reader:&Love Vanderwalle\footnote{Assistant Professor of Economics, The Graduate Institute, Geneva; lore.vandewalle@graduateinstitute.ch}
%\end{tabular}
%}

@@

\addbibresource{bibliography.bib}

@@

\subfile{surviving.tex}

@@

\subfile{morrisShin.tex}

>>>>

\title{Preliminary Thesis Defence\\~\\
\begin{tabular}{rl}
Supervisor:&Jean-Louis Arcand\footnote{Professor of Economics, The Graduate Institute, Geneva; Director, Centre for Finance and Development; jean-louis.arcand@graduateinstitute.ch}\\
Second Reader:&Love Vanderwalle\footnote{Assistant Professor of Economics, The Graduate Institute, Geneva; lore.vandewalle@graduateinstitute.ch}
\end{tabular}
}

@@

\addglobalbib{bibliography.bib}

@@

\begin{refsection}
\subfile{surviving.tex}
\printbibliography
\end{refsection}

@@

\begin{refsection}
\subfile{morrisShin.tex}
\parencite{morris1998unique}
\printbibliography
\end{refsection}
